The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-05 paper/introduction.tex
WIP paper commit

A group of astronomers wants to measure the mean number of planets of a 
certain type per star of a certain type.
Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
survey and detect $N_{\rm det}$ signals that seem to be from the desired 
class of planet.
They count the apparent number of selected stars, $N_\star$.
Assuming their survey is limited by Poisson noise, the group computes
their detection efficiency $p_{\rm det}$ as a function of planetary and 
stellar properties, in order to know which of the selected stars were
searchable.
Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
apparent occurrence rate $\Lambda_{\rm a}$:
\begin{equation}
\Lambda_{\rm a} = \frac{N_{\rm det}}{N_\star} \times \frac{1}{p_{\rm tra}}
								  \times \frac{1}{p_{\rm det}}.
\label{eq:wouldnt_it_be_nice}
\end{equation}

@@

Outside of astrophysical differences, there are observational biases for every 
term in Eq.~\ref{eq:wouldnt_it_be_nice}.
There are errors in $N_{\rm det}$ due to planet radius misclassification.
There are errors in $N_\star$ because a given selected star might in fact be 
two stars.
There are errors in $p_{\rm tra}$ because stars in binaries may have different 
masses and radii than assumed in the single-star case.
Finally, there are errors in $p_{\rm det}$ because detection efficiencies 
for planets orbiting single stars, primaries, and secondaries are all 
different.

>>>>

A group of astronomers wants to measure the mean number of planets of a 
certain type per star of a certain type.
Ignoring stellar multiplicity, they perform a signal-to-noise limited transit 
survey, and detect a set of planets that appear to be of the desired class.
They then choose the stars (among those initially surveyed) around which the 
planets of interest appeared to be searchable.
Correcting for the geometric transit probability $p_{\rm tra}$, they report an 
apparent rate density,
\begin{equation}
\Gamma\a(\pp\a, \ps\a) = \frac{N_{\rm det}(\pp\a, \ps\a)}{N_{\rm s,a}(\pp\a, 
    \ps\a)} \times \frac{1}{p_{\rm tra}(\pp\a, \ps\a)}.
\label{eq:wouldnt_it_be_nice}
\end{equation}
where $\pp\a$, $\ps\a$ are the apparent planetary and stellar parameters, 
respectively.
Here $N_{\rm det}(\pp\a, \ps\a)$ is the number of 
detected planets with parameters $\pp\a,\ps\a$, per unit $\pp\a$ and $\ps\a$. 
The quantity $N_{\rm s,a}(\pp\a, \ps\a)$ is the number of unresolved 
point-sources on the sky the appear to be searchable.

@@

Outside of astrophysical differences, there are observational biases for every 
term in Eq.~\ref{eq:wouldnt_it_be_nice}.
There are errors in $N_{\rm det}$ due to planet radius 
misclassification.
There are errors in $N_{{\rm s,a}}$ because a given point on the sky
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars (but see Sec.~\ref{sec:model_1} for discussion of why this is 
a second-order effect).

Finally, there are errors in $p_{\rm det}$ because detection efficiencies 
for planets orbiting single stars, primaries, and secondaries are all 
different.
